Vragenlijst thesis evaluatie

### 2015-05-14 doc/template/chap-5.tex
Case 2 geschreven
bib file in orde !

Gametheory is a mathematical study to analyse interactions between independent and self-interested agents. To get an understanding of the most important concepts of game theory, a short introduction based on the work of 
\citep{leyton2008essentials} and \todo{Coursera} is given in section 2.1 [] \todo{ref}. For a more detailed and full introduction to game theory, the reader is referred to 
\todo{leyton2008essentials}.  In section 2.2 [] \todo{ref} an overview of the FlipIt game is given with the definitions and concepts that will be used throughout the paper.
The last section [] \todo{ref} will cover the extensions and additions already made on FlipIt.

@@

%There are two standard representations for games. The first one is the Normal Form. The second one is the Extensive Form.

In the following list a couple of terms that will be used throughout the paper.
\begin{description}
\item \textit{Players}: Players are referred as the ones who are the decision makers. It can be a person, a company or an animal.  (they will act rational )
\item \textit{Actions}: Every player has actions that he or he can do. 
\item \textit{Strategies}: A strategy is the combination of different actions. A pure strategy is only one action.
\item \textit{Utility function}: The utility function is the mapping of the level of happiness of an agent about the state of the world to natural numbers.

>>>>

Gametheory is a mathematical study to analyse interactions between independent and self-interested agents. To get an understanding of the most important concepts of game theory, a short introduction based on the work of 
\cite{leyton2008essentials} and \todo{Coursera} is given in section 2.1 [] \todo{ref}. For a more detailed and full introduction to game theory, the reader is referred to 
\cite{MitigationCovert}.  In section 2.2 [] \todo{ref} an overview of the FlipIt game is given with the definitions and concepts that will be used throughout the paper.
The last section [] \todo{ref} will cover the extensions and additions already made on FlipIt.

@@

%There are two standard representations for games. The first one is the Normal Form. The second one is the Extensive Form.
\subsubsection{List of terms}
In the following list a couple of terms that will be used throughout the paper.
\begin{description}
\item \textit{Players}: Players are referred as the ones who are the decision makers. It can be a person, a company or an animal.  (they will act rational )
\item \textit{Actions}: Every player has actions that he or he can do. 
\item \textit{Strategies}: A strategy is the combination of different actions. A pure strategy is only one action.
\item \textit{Utility function}: The utility function is the mapping of the level of happiness of an agent about the state of the world to natural numbers.
